Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-23 awipev-CO2.Rmd
commented unnecessary code

ts_sal / ts_temp / ts_at
grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
```

>>>>

# ts_sal / ts_temp / ts_at
# grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
# cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
# multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
```
